When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-03-26 doc/paper/vpd_et_paper.tex
addeds econd derviative plot, should probably hash it to save ink, also need to write that section

Lastly, our paper builds important intuition for how plants will respond to VPD pertubations, including expected increases in VPD induced by global change.  Plant physiological responses to direct CO$_2$ effects \citep[e.g.,][]{Swann_2016} receives more attention than physiological response to indirect effects like increased VPD. Here, we provide broad PFT-focused results showing a likely decrease in ET in response to positive VPD perturbations (atmospheric drying), which is consistent with recent observational analysis \citep[e.g.,][]{Rigden_2017}. Feedbacks between the land and the atmosphere may alter the net response to a global VPD perturabation, but our focus on the one way plant response to a VPD perturbation in the atmopsheric boundary layer is an important first step to disentangling such feedbacks, both in observations and model simulations of the present and future. By removing Penman Monteith's dependence on implicit relationships between GPP, VPD, and ET, we allow for explicit, accuruate analysis of plant-VPD feedbacks in the atmospheric boundary layer (Equation \ref{et}). Our approach can be extended to examine varying plant response to more nuanced consideration of plant type and climate. Any plant physiological heterogeneity that can be conceptualized with shifts in $g_1$ \citep[e.g.][]{Lin_2015, Medlyn_2017} and/or uWUE \citep[e.g.][]{Zhou_2014} is representable within our framework, which opens the door for a hierarchy of more sophisticated climate- and plant-specific analysis of ET sensitivity to environmental variables (including VPD). We argue that such simplified conceptual frameworks are critical tools for disentangling land-atmosphere feedbacks at various scales, from diurnal to seasonal and beyond, and to characterize ET response in a warmer, atmospherically drier, and enriched CO$_2$ world.

>>>>

Lastly, our paper builds important intuition for how plants will respond to VPD pertubations, including expected increases in VPD induced by global change.  Plant physiological responses to direct CO$_2$ effects \citep[e.g.,][]{Swann_2016} receives more attention than physiological response to indirect effects like increased VPD. Here, we provide broad PFT-focused results showing a likely decrease in ET in response to positive VPD perturbations (atmospheric drying), which is consistent with recent observational analysis \citep[e.g.,][]{Rigden_2017}. Feedbacks between the land and the atmosphere may alter the net response to a global VPD perturabation, but our focus on the one way plant response to a VPD perturbation in the atmopsheric boundary layer is an important first step to disentangling such feedbacks, both in observations and model simulations of the present and future. By removing Penman Monteith's dependence on implicit relationships between GPP, VPD, and ET, we allow for explicit, accuruate future analysis of plant-VPD feedbacks in the atmospheric boundary layer (Equation \ref{et}). Our approach can also be extended to examine varying plant response to more nuanced consideration of plant type and climate. Any plant physiological heterogeneity that can be conceptualized with shifts in $g_1$ \citep[e.g.][]{Lin_2015, Medlyn_2017} and/or uWUE \citep[e.g.][]{Zhou_2014} is representable within our framework, which opens the door for a hierarchy of more sophisticated climate- and plant-specific analysis of ET sensitivity to environmental variables (including VPD). We argue that such simplified conceptual frameworks are critical tools for disentangling land-atmosphere feedbacks at various scales, from diurnal to seasonal and beyond, and to characterize ET response in a warmer, atmospherically drier, and enriched CO$_2$ world.
